Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
+bib system

%% Abstract section.
\abstract{
Vega-Lite is a high-level grammar which is easy to understand. Naturally,
the user base of Vega-Lite ranges from beginners to experts in the field of
visualization. Although users with less JSON experience have no trouble working
with most of the features of Vega-lite, composing different views together has
a sharp learning curve. View composition requires a good understanding of tree
structure since different views can be nested inside each other to create more
complex views.

@@

Although Vega-Lite aims to be easy to use for users with a non-computer science
background, view composition is one of the aspects that can be difficult to work
with. Since Vega-Lite~\cite{notes2002} specification is in JSON format, when users
want to nest view composition, inner specifications have to be nested heavily.
However, mapping from the design in the user’s mind to JSON nested structure is
hard because JSON does not well represent the layout of the composite views.

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{template}
\end{document}

>>>>

%% Abstract section.
\abstract{
  Vega-Lite~\cite{2017-vega-lite} is a high-level grammar which is easy to understand. Naturally,
the user base of Vega-Lite ranges from beginners to experts in the field of
visualization. Although users with less JSON experience have no trouble working
with most of the features of Vega-lite, composing different views together has
a sharp learning curve. View composition requires a good understanding of tree
structure since different views can be nested inside each other to create more
complex views.

@@

Although Vega-Lite aims to be easy to use for users with a non-computer science
background, view composition is one of the aspects that can be difficult to work
with. Since Vega-Lite specification is in JSON format, when users
want to nest view composition, inner specifications have to be nested heavily.
However, mapping from the design in the user’s mind to JSON nested structure is
hard because JSON does not well represent the layout of the composite views.

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{paper.bib}
\end{document}
